A Bayesian model for the K2 data

### 2013-11-03 text/prob_model/prob_model.tex

Estimates for the posteriors over weights for target-related controls
are plotted in Figure~\ref{fig:Posterior_TF}. The results are exactly
as we would expect them to be. Given our data, we should believe that
the late-closure reading is more prominent. But the level of
prominence varies with accentuation. Under prosody that we
hypothesized would favor the late-closure reading, the contrast is
most pronounced. Contrarily, accentuation that we hypothesized favors
the early-closure reading we are no longer justified in believing that
the late-closure reading is certainly preferred (witness the clearly
overlapping 95\% confidence regions).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/Posterior_T.pdf}
  \caption{Posteriors over weights for target readings in critical
    conditions. Colored lines below the actual plots indicate 95\%
    confidence intervals.}
  \label{fig:Posterior_T}
\end{figure}

Turning to the critical conditions, estimates of posteriors over
weights given our data are given in Figure~\ref{fig:Posterior_T}. We
only have marginal reasons to believe that global readings have any
non-negligible weight data in the AS-A condition. Apart from this, if
the model is true, the data corroborates the belief that the literal
reading is strongly preferred over the local reading over the global
reading (again witness the non-overlapping 95\% confidence
regions). We also see the expected general effect of intonational
markedness. Qualitatively speaking, the preference for literal
readings appears less pronounced in the accented conditions.

@@

>>>>

Estimates for the posteriors over weights for target-related controls
are plotted in Figure~\ref{fig:Posterior_TF}. The results are exactly
as we would expect them to be. Given our data, we should believe that
the late-closure reading is more prominent. But the level of
prominence varies with accentuation. Under prosody that we
hypothesized would favor the late-closure reading, the contrast is
most pronounced. Contrarily, accentuation that we hypothesized favors
the early-closure reading we are no longer justified in believing that
the late-closure reading is certainly preferred (witness the clearly
overlapping 95\% HDIs).\footnote{A 95\% Highest Density Interval (HDI)
  is a convex region of values over which 95\% of the distribution's
  probability density is divided, such that no value outside of that
  region has higher probability density than any point within
  \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
  HDI is the set of values into which we should believe most strongly,
  and what falls outside this region is what can be excluded with
  relative safety.}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pics/Posterior_T.pdf}
  \caption{Posteriors over weights for target readings in critical
    conditions. Colored lines below the actual plots indicate 95\%
    HDIs.}
  \label{fig:Posterior_T}
\end{figure}

Turning to the critical conditions, estimates of posteriors over
weights given our data are given in Figure~\ref{fig:Posterior_T}. We
only have marginal reasons to believe that global readings have any
non-negligible weight data in the AS-A condition. Apart from this, if
the model is true, the data corroborates the belief that the literal
reading is strongly preferred over the local reading over the global
reading (again witness the non-overlapping 95\% HDIs). We also see the expected general effect of intonational
markedness. Qualitatively speaking, the preference for literal
readings appears less pronounced in the accented conditions.

@@

\paragraph{Hypothesis testing.} We are interested in two questions:
(i) which readings are available? and (ii) what is the preference
order over readings?

The first question can be answered by looking at the HDIs of the
posteriors of the candidate readings. The HDIs give the region of the
95\% least unbelievable parameter values, given the data and the
model. We would like to check the hypothesis that a given reading is
unavailable, i.e., it's activation value in the probabilistic model is
equal to 0, or close to zero, i.e., within a small distance away from
the critical value, such as $0.01$ (Region of Practical Equivalence,
ROPE). We reject the ``null-hypothesis'' that the true value is 0 if
its ROPE lies entirely outside the 95\% HDI; we accept the
``null-hypothesis'' if the ROPE lies entirely within the 95\% HDI
\citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following table
lists approximations of the 95\% HDIs for each condition and reading:

\begin{center}
  \begin{tabular}{lllllll}
    & lit & loc & glb & \\ \midrule
    as-n & $(0.8595 , 0.9796)$ & $(0.017 , 0.1321)$
    & $(0 , 0.021)$ \\
    as-a 
    & $(0.7633 , 0.9312)$
    & $(0.0564 , 0.2063)$
    & $(0 , 0.0639)$ \\
    es-n 
    & $(0.664 , 0.9502)$
    & $(0.0486 , 0.3329)$
    & $(0 , 0.0254)$ \\
    es-a 
    & $(0.5688 , 0.7998)$
    & $(0.1987 , 0.4294)$
    & $(0 , 0.0199)$ 
  \end{tabular}
\end{center}

For a ROPE of up to $[0;0.017)$ we therefore should draw the same
conclusion for all conditions: we reject the hypothesis that there are
no local readings, but we neither accept nor reject the hypothesis
that there are no global readings.

The second question after the preference relations between readings
can be answered in a similar way. Here, we look at the posterior
beliefs about the differences of activation strengths and ask whether
these posterior beliefs allow us to safely conclude that differences
are bigger than zero or not. Figure~\ref{fig:PostDiffT} shows the
relevant comparisons, together with the 95\% HDIs showing that the
data provides evidence that the qualitative preference order is the
same in all conditions: literal readings are preferred over local
readings, which are in turn preferred over global readings.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{PostDiffT.pdf}
  \caption{Posteriors over differences between activation strengths.}
  \label{fig:PostDiffT}
\end{figure}
